\chapter{Glossaries and Acronyms}
\section{Glossaries}
\textbf{Application programming interface} - An API, or application programming interface, is a set of rules that define how applications or devices can connect to and communicate with each other (\cite{rest_api}).

\textbf{Artificial intelligence} - A field which combines computer science and robust datasets to enable problem solving (\cite{artificial_intelligence}).

\textbf{Cloud computing} - Delivery of IT resources over the internet such as data storage, servers and software.  

\textbf{Edge computing} - A distribution architecture where processing and data storage are brought closer to the data source to prevent servers overloading from handling vast loads of data.  

\textbf{Hypertext transfer protocol} - A protocol for transferring data between network devices.

\textbf{InfluxDatabase} - A time series-database which provides SQL-like syntax that is quick to query resources. Time-series database automaticly includes timestamp for each databse entry. 

\textbf{Internet of Things} - The Internet of Things refers to physical objects that communicate using sensors, cameras, software, or other technologies connecting and exchanging data. 

\textbf{Internet of Vehicles} - An IoV system is a distributed system for wireless communication and information exchange between vehicles through agreed-upon communication protocols \parencite{chinese_iov}.

\textbf{Raspberry Pi} - A series of small single-board computers developed by the RaspBerry Pi foundation. 

\textbf{Remote procedure call} - A protocol that provides the high-level communications paradigm used in the operating system. RPC presumes the existence of a low-level transport protocol, such as Transmission Control Protocol/Internet Protocol (TCP/IP) or User Datagram Protocol (UDP), for carrying the message data between communicating programs. \parencite{rpc_ibm}

\textbf{Representation state stransfer} - An architectural style when used together with API, provides communication through HTTP.

\textbf{Tensor Processing Unit} - Tensor Processing Units (TPUs) are Google’s custom-developed application-specific integrated circuits (ASICs) used to accelerate machine learning workloads \parencite{google_tpu}.

\textbf{Transmission control protocol} - A protocol that ensures reliable delivery of data over the internet.

\textbf{Websockets} - Websockets is a protocol that provides a bidirectional communication between clients and server by establishing a single TCP connection in both direction \parencite{rfc_websockets}.     

\section{Acronyms}
\textbf{AI} - Artificial intelligene

\textbf{API} - Application programming interface

\textbf{CRUD} - Create, read, update, and delete

\textbf{HTTP} - Hypertext transfer protocol

\textbf{IDE} - Integrated Development Enviroment

\textbf{IoT} - Internet of things

\textbf{IoV} - Internet of vehicles

\textbf{REST} - Representational state transfer

\textbf{RPC} - Remote procedure call 

\textbf{SQL} - Structured query language

\textbf{TCP} - Transmission control protocol

\textbf{TPU} - Tensor processing unit

\textbf{UML} - Unified modeling language