\section{Machine learning}
Machine learning is a subfield of artificial intelligence, which is broadly defined as the capability of a machine to imitate intelligent human behavior \parencite{ml_explained}.

There are three types of machine learning, supervised learning, unsupervised learning and reinforcement learning. In supervised machine learning the algorithm is given labeled data to help predict outcomes. This means the algorithm uses already historical data. Supervised learning is the most commonly used machine learning. Supervised learning can be separated into 2 different problems when data mining, classification and regression \parencite{delua_ibm}. Classification uses an algorithm that assigns test data into the right categories. For example, differentiate between cats and dogs. Regression is another type of supervised learning method that uses an algorithm to understand the relationship between dependent and independent variables \parencite{delua_ibm}. Regression is used for predicting mathematical values such as stocks and sales. The prior group used supervised learning to train their camera detection model. 

However in unsupervised learning the algorithm uses non-labeled data. The algorithm looks for patterns or trends in the data. This can be used for labeling data or figuring out trends. Customers that buy item x will be more likely to buy item y as well.

Reinforcement learning trains the machine via trial and error and a reward system. This is commonly used to train machines in games or autonomous vehicles. An example is Stockfish 14, one of the best chess engines in the world. (kilde)


About four of five traffic accidents are caused by human error \parencite{policy_advise}. And in fields that require a specific task to be done, for example chess ai, already surpasses humans. This means if an learns to drive perfectly, four out of five traffic accidents can be avoided. However driving is a complex task that requires a ton of data, and decision making. In addition, for an Ai to give the most accurate outcome a lot of accurate test data are required. Nearly 43\% of people in the US are afraid of self-driving cars \parencite{kopestinsky}. Giving a self-driving car an accurate driving environment without risking human lives is therefore a challenge.