\section{Phase 1 - Planning and research phase}\label{sec:phase1}

After we had gotten in touch with Accenture and spoken with the supervisors and the product owner, the group had to make a few decisions regarding the project's direction.

An important choice for the project was to either build and train an AI model for the vehicles from scratch or use the existing model. Building a new AI model would provide a deeper understanding of the model we could utilize. Due to the time constraint, we determined that it was more favorable to continue with the existing model. In addition, we believed that the project would have the potential to be too similar to the previous project.  Our group also had more prior experience with networking than with Raspberry Pi and AI. We, therefore, chose to use the AI model from the previous project. 

In this phase, we did not have access to the vehicle, nor the code, made by the prior bachelor group. However, there was a need for project planning and research before we could start developing our IoT system anyway. The topics that needed to be researched were:

\begin{itemize}
\item What causes traffic jams and solutions to fix it.
\item IoT-systems and how they function with vehicles.
\item Planning and development methods that will fit our project
\end{itemize}

We also used the pre-project phase to get to know Accenture, their guidelines, and their workspace. Moreover, we participated in a "Design thinking"-workshop. 

%\subsection{Design thinking workshop}



\input{chapters/sections/subsections/programming_language}

\input{chapters/sections/subsections/artificial_intelligence_and_Internet_of_things}

\input{chapters/sections/subsections/Increasing_trafficflow_for_one_lane_road}
\clearpage