\section{Essential code snippets behind the system}
The central part of this project is to develop a client-server communication system to produce a physical simulation of how a centralized system can contribute to an improved traffic flow. Due to the nature of this project, working with physical models, no graphical user interfaces have been developed. Hence, it is necessary to present critical parts of the code that are responsible for such a system to work. This section will elaborate, in detail, on how essential code snippets interact with each to produce the result.

Furthermore, the code written in this project is in the languages Python and C\# using Pycharm and Rider IDE, respectively. Therefore, syntax highlighting is used throughout this section to best simulate the same syntax highlighting used in both IDE, respectively. 

In addition, some artistic freedom has been used to present the code snippets; the symbol \verb|...| has been used to indicate irrelevant code to the current discussion, and the symbol  \textcolor{red}{$\hookrightarrow$} simply means that the line of code following \textcolor{red}{$\hookrightarrow$} is on the same line above but is broken up due to lack of space. Also, each code snippet starts with the class and method that belongs to it. The user manual, in \secref{sec:user_manual}, is written following the same style as this section.
\input{chapters/sections/subsections/initialization}
\input{chapters/sections/subsections/handshake_and_listener}
\input{chapters/sections/subsections/patching}
\input{chapters/sections/subsections/database}
\input{chapters/sections/subsections/route_planner}