\section{Tools and technologies}
The circumstances surrounding Covid 19 meant that we could not meet our supervisors in person at the start. Luckily, the group could still meet physically a few times a week. We had to use a wide range of tools for communication. Most restrictions were removed later in the project, but we kept our meetings with our supervisors digital throughout the project. 

\begin{itemize}
	\item Email - Formal communication with supervisors and product owner
	\item Teams - Meetings, and the platform of choice for communicating with the external supervisors on an informal level. 
	\item Zoom - Meetings with our internal supervisor at OsloMet
	\item Facebook Messenger - Communication internally in the group. We used it to send messages to each other when we were not physically together, and to send pictures of code. 
\end{itemize}

The project required us to collaborate while working on different computers, leading to potential overlapping. Therefore, tools that helped us work on the project together were essential. We used the following tools for this purpose:

\begin{itemize}
	\item Git and Github - Version control of choice
	\item Google docs - Used to write our journal and other documents that need to get updated regularly, and to share documents. 
	\item Latex - Used to write reports.
\end{itemize}

We also needed text editors that supported the programming languages that we used. Our solution was created with Python and C\#.
\begin{itemize}
	\item Pycharm - IDE for coding in Python
	\item Visual studio and Rider - IDE for coding in C\#
	\item Thonny - Text editor for coding in Python on Raspberry pi
\end{itemize}

Project planning and documentation were also an important part of the project. The tools we used for the project planning were:

\begin{itemize}
	\item Github project - Kanban board and creating backlog tasks
	\item Excel - Used for visualizing our workplan with tables and a Gantt diagram
\end{itemize}