\chapter{Conclusion}
\section{Results}
In regards to the problem statement in \secref{sec:problem_statement} and the goals for this project discussed in \secref{sec:goals}, we have been able to successfully create a centralized system that can communicate with autonomous vehicles. A significant change in velocity can lead to a disruption of traffic flow, as discussed in \secref{sec:traffic_congestion}. Through multiple semi-physical demonstrations discussed in \secref{sec:demo}, it was apparent that the server was able to contribute to an improved traffic flow by preemptively reducing vehicles' to the necessary speed to prevent collisions. Even though this project did only account for scenarios involving intersections, it is also, from the exploration done throughout this project, clear that autonomous vehicles, together with a centralized system, can contribute to improving traffic flow in the future.

Furthermore, we received positive feedback after showing our supervisors and product-owner video snippets of the conducted demonstrations. The product owner also confirmed that our results adhered to the requirements set by Accenture.

\input{chapters/sections/subsections/real_world_scenario}
\input{chapters/sections/subsections/possible_improvements}

\section{Further discussions}
In addition to implementing the program, we also had discussions regarding the viability of the program. Here we will discuss our process and how such an IoT system would apply to the real world. We will use our data and some research to reflect the usability of an IoT system where self-driving cars can communicate with each other.

\input{chapters/sections/self_evaluation}
\input{chapters/sections/further_work}